---
title: "Cluster Visuations"
author: "Robin Burke"
date: "1/8/2017"
output: html_document
params:
  username: "oboc_read"
  password: ""
---

This file displays several visualizations of the principal components clustering of the library branches.

```{r}
library(knitr)
setwd("/home/rburke/oboc/src/rcr-analysis/src/viz/")
read_chunk("cluster-viz.R")
```

### Project constants

```{r C1}
```

### Load libraries

```{r C2}
```

### Loading the principal components data

```{r C3}
```

### Load the cluster table

```{r C4}
```

### Load the library locations for the map

```{r C5}
```

### Load the shape files for the map

```{r C6}
```

### Associate clusters with locations

```{r C7}
```

### Convert shape files 

```{r C8}
```

### Branch map, colored by cluster

```{r C9}
```

### Data frame for multi-dimensional scaling

```{r C10}
```

### Compute distances

```{r C11}
```

### Plot 2-D projection

```{r C12}
```

### Compute mean component value for each cluster
Contrast with medoids from cluster.Rmd

```{r C13}
```

### Plot the weights for each cluster

```{r C14}
```

Similar results to the medoids.

Cluster 1 is poorer, but mostly non-diverse with more renters, more folks close to work or unemployed. 

Cluster 2 is wealthier with more housing mix, public transit users.

Cluster 3 is poorer and more Latinx residents, but homeowners.

Cluster 4 is similar to cluster 3, but with slightly lower property values, possibly because of rental units, larger black population.

Cluster 5 is affluent neighborhoods, mostly white residents. 


