---
title: "Time Series Plots"
author: "Robin Burke"
date: "7/23/2017"
output: html_document
params:
  username: "oboc_read"
  password: ""
---

This file displays time series visualizations of circulation

```{r}
library(knitr)
setwd("/home/rburke/oboc/src/rcr-analysis/src/viz")
read_chunk("time-series.R")
```

### Project constants

```{r C1}
```

### Load libraries

```{r C2, warning=FALSE, message=FALSE}
```

### Database connection

```{r C3}
```

### Database query

```{r C4}
```

### Daily circulation

```{r C5}
```

### Daily circulation smoothed

```{r C6, fig.width=10}
```

A couple of points.

- Our Augie March data looks like it is cut off. I think this is because there are days with no check-outs in the whole system.
- Adding the correct announcement days changes the relation between WS / BT and the other books. The peaks correspond to the fall programming, but the ramp up commences with the announcement.

### Checkout density

```{r C7}
```

### Build weekly aggregation

```{r C8}
```

### Weekly circulation

```{r C9, fig.width=10}
```
