---
title: "Multi-level Model Normalized"
author: "Robin Burke"
date: "7/23/2017"
output: html_document
params:
  username: "oboc_read"
  password: ""
---

This file computes a multi-level linear model of the circulation per 1k visitors data against the library data represented as the principal components of the demographic representation and the book holdings.

```{r}
library(knitr)
setwd("/home/rburke/oboc/src/rcr-analysis/src/model/")
read_chunk("multi-level-norm.R")
```

### Project constants

```{r C1}
```

### Load libraries

```{r C2}
```

## Loading the data

### Library data including principal components

```{r C3}
```

### Connect to database

```{r C4}
```


### OBOC circulation data


```{r C5}
```


### Holdings data

```{r C6}
```

### Get book-year table from the database

```{r C7a}
```

### Compute book-wise branch circulation

As it turns out, this series is pretty closely correlated with the library holdings for each book. (Perhaps not surprising as this is likely how titles were/are allocated.)

Scale to the range closer to the principal component values

```{r C7b}
```

### Compute book-wise branch visitors

Scale to the range closer to the principal component values

```{r C7c}
```

### Perform joins

```{r C8}
```

### Create data subsets

PW is dropped because it has no visitor data on the City of Chicago site. We create a square transform of PC2. This produces a more linear response in the circulation values.

```{r C9}
```

Total circulation

```{r P1}
```

## Lattice plots full data

Plot the checkout frequency against the model variables.

### Holdings

```{r LPFull1}
```

### Total branch visitors

```{r LPFull2}
```

### Principal component 1

```{r LPFull3}
```

### Principal component 2 (square transform)

```{r LPFull4}
```

### Principal component 2 (untransformed)

Not obvious non-linearity

```{r LPFull4a}
```

### Principal component 3

```{r LPFull5}
```

### Principal component 4

```{r LPFull6}
```

## Models

### Simple linear model

```{r M1}
```

### Book-only effects

```{r M2}
```

### Branch-only effects

```{r M3}
```

### Full model

```{r M5}
```

### Fixed effects

```{r C13}
```

### Random effects

```{r C14}
```

## Examining the coefficients

```{r C15}
```

```{r C16}
```

### Principal components

```{r PCoef1}
```

### Holdings

```{r PCoef2}
```

### Intercepts

```{r PCoef3}
```

