---
title: "Demographic Clustering"
author: "Robin Burke"
date: "1/8/2017"
output: html_document
params:
  username: "rburke"
  password: ""
---

This file computes a clustering of the library branches based on principal components.

```{r}
library(knitr)
setwd("/home/rburke/oboc/src/rcr-analysis/src/demographic")
read_chunk("cluster.R")
```

### Project constants

```{r C1}
```

### Load libraries

```{r C2}
```

### Loading the principal components data

```{r C3}
```

### Drop unused rows and columns
Remove non-demographic columns. Remove regional libraries as their demographics are just aggregations of the others.
Create two data frames with 16 and 8 components, respectively.

```{r C4}
```


## Clustering computation

### A function to try clusterins
Using PAM - Partitioning Around Medoids.

```{r C5}
```

### k=3, 16 components


```{r C6}
```

### k=4

```{r C7}
```

### k=5

```{r C8}
```

### k=6

```{r C9}
```

### k=7

```{r C10}
```

The silhouette value peaks at k=5. Now trying with a smaller number of PCs. Perhaps less noise.

### k=4, 8 components


```{r C11}
```

### k=5

```{r C12}
```

### k=6

```{r C13}
```

### Choosing k = 5, with PC = 8
Adding back in the regional libraries as cluster 6.

```{r C14}
```

### Saving

```{r C15}
```

### Examining the medoids
Note that the transform of PC2. This is the same transformation applied in the 
multi-level model. High PC^2 value reflects larger number of black and / or Latinx residents. 


```{r C16}
```

### Plot of component weight in each cluster

```{r C17}
```

Cluster 1 is diverse with more renters, more folks close to work or unemployed. 

Cluster 2 is more white with more homeowners, public transit users.

Cluster 3 is poorer and more Latinx residents, but homeowners.

Cluster 4 is similar to cluster 3, but with African-American residents, slightly greater property values, possibly because of rental units.

Cluster 5 is affluent neighborhoods, mostly white residents. 

Note also that these are mediods -- particular branch areas that are representative of their clusters. A better visualization would be to show the distribution of each component in the clusters. See cluster-viz.Rmd

## Updating database

### Set up
```{r C18}
```

### Connect to database
```{r C19}
```

### Write cluster table
```{r C20}
```

### Update branch table
```{r C21}
```

### Clean up
```{r C22}
```


