---
title: "Principal Components"
author: "Robin Burke"
date: "1/8/2017"
output: html_document
---

Creates a principal components representation of the demographic data.

Load the code from the R file

```{r}
library(knitr)
setwd("/home/rburke/oboc/src/rcr-analysis/src/demographic")
read_chunk("components.R")
```

### Load project constants

```{r C1}
```

### Load libraries

```{r C2}
```

### Load demographic data

```{r C3}
```

### Extract demographic features

Skip the library features, such as circulation and visitors

```{r C4}
```

### Remove features with high correlations

```{r C5}
```

### Remove columns with low incidence

Less than 1% of population

```{r C6}
```

### Compute principal components

```{r C7}
```

### Component heat map

This function display a one-column heat map of one of the principal components
showing the contribution of each demograpic feature. The threshold removes
dimensions with a smaller contribution.

```{r}
componentMap <- function(comp, thresh)
{
  overThresh <- which(abs(comp)>thresh)
  comp.filtered <- comp[overThresh]
  comp.filtered <- comp.filtered[order(comp.filtered, decreasing=FALSE)]
  
  df <- data.frame(x=c("Component"),
                   y=factor(names(comp.filtered), levels=names(comp.filtered)),
                   value=comp.filtered)

  p <- ggplot(df, aes(x=x, y=y, fill=value))
  p <- p + geom_tile()
  p <- p + labs(x="",y="")
  p <- p + scale_x_discrete(expand=c(0,0))
  p <- p + scale_fill_gradientn(name="",
                      colours=colorRampPalette(c('blue', 'white', 'red'))(12))
  print(p)
}
```

### Principal component 1

```{r}
componentMap(features.components$rotation[,1], 0.1)
```

Note the strong (positive) contribution for:

- Unemployed (PCT16Unemp)

Note the strong (negative) contribution for:

- Median property value (MedPV)
- White residents (PCTWhite)
- Private school attendance (PCT3PvtSch)

This axis has to do with affluence.

```{r}
componentMap(features.components$rotation[,2], 0.1)
```

Note the strong (positive) contribution for:

- Black residents (PCTBlack)
- Workers in education (PCTioEdu)

Note the strong (negative) contribution for:

- Male residents (PCTMale)
- Hispanic residents (PCTHispLat)
- Construction workers (PCTioCnstr)

This axis corresponds to the division between Hispanic and Black areas.

```{r}
componentMap(features.components$rotation[,3], 0.1)
```

Note the strong (positive) contribution for:

- Owner-occupied housing (PCTHUOocc)
- Percent about poverty level (PCT_APL)
- Residents between 35-64 (PCTAg35_64)

Note the strong (negative) contribution for:

- Percent never married (PCT15Nmary)

This axis corresponds to more established households, older home-owning residents.

```{r}
componentMap(features.components$rotation[,4], 0.1)
```

Note the strong (positive) contribution for:

- Time to work less than 30m (PCTtLT10m, PCTtl10_29m)
- Walk to work (PCTmtwwalk)

Note the strong (negative) contribution for:

- Longer commute time (PCTt30_59m)
- Public transport and El usage (PCTmtwEL, PCTmtwpubT)

This axis corresponds to commuters vs people who live near where they work.

### Create a data frame with the transformed features

We keep the first 16 principal components

```{r C8}
```

### Save the data

```{r C9}
```

### Save the principal components computation

```{r C10}
```

