---
title: "Demographic Data"
author: "Robin Burke"
date: "1/8/2017"
output: html_document
---


Load the code from the R file
```{r}
library(knitr)
setwd("/home/rburke/oboc/src/rcr-analysis/src/demographic")
read_chunk("demographic.R")
```

Load project constants

```{r C1}
```

```{r C2}
```

Create a new column for the percentage of the population that is registered to vote.

```{r C3}
```

Drop the columns that we do not use. These are:

- The monthly circulation columns. It might be possible to integrate these into time series analysis.
- The monthly visitor columns.
- All columns that are not normalized by population or tract size. This is necessary because the polygons are very different in population. We can only use the percentage-based columns.

```{r C4}
```

Drop the rows that we do not use. These are:

- The 'bookkeeping' branches such as the Bookmobiles.
- The main and regional libraries as represented by their local areas.

The list is stored in the BRANCHES_IGNORABLE variable.

```{r C5}
```

Save the file in branch-data-reduced-yyyymmdd.csv

```{r C6}
```
